Progress Report for CSS 586 Project: \\ Music Generation Using Deep Learning

### 2021-05-04 papers/progress/jack/progress-jack.tex
Update to Jack's report

@@

\section{Progress}
Talk about learning of RNN, GRU, and LSTM
Talk about data exploration

>>>>

Musical generative modeling is an interesting area of research. Recent innovations in this domain involve
deep learning using a variety of modelling techniques. This section presents some of the recent works in
this domain.

Historically, the modelling of raw audio data is extremely challenging because a single second of audio recording
could contains up to 44,100 samples in the case of music. Google DeepMind's WaveNet is one of the first models
that successfully learn from raw audio data \cite{oord_wavenet_2016}. It is designed using a technique called 
1D dialated causal convolution that allows an output to capture information from many inputs with a minimal
computational cost. WaveNet was designed for the primary purpose of generating speech which mimics any human voice.
However, since the architecture can be used to model any raw audio signal, it was also used to generate music.
Although the outputs were far from being any masterpieces, the results show the possibility of generating musical
pieces from the raw audio data.

@@

\section{Progress}
